That's No Moon: New Analysis Shows No Evidence for Lunar Companion Orbiting Kepler-1625b

### 2019-01-23 ms-temp.tex
v1

\begin{abstract}
    Observations of the Kepler-1625 system with the Kepler and Hubble Space Telescopes have suggested the presence of a candidate exomoon, a Neptune-radius satellite orbiting a long-period Jovian planet. Here we present a new analysis of the Hubble observations from an independent data reduction pipeline. We find that the transit light curve is well fit with a planet-only model, and that the addition of a moon does not significantly improve the fit quality. The $3\,\sigma$ upper limit on the moon radius is $4.0R_\oplus$. FIXME: why are we different from TK18?  We conclude that FIXME, and future follow-up efforts for exomoons should focus on alternative targets.
\end{abstract}

\keywords{planets and satellites: individual (Kepler-1625b)}

@@

Recently, a potential exomoon candidate was identified in the Kepler-1625 system \citep{teachey18a}. The host planet, Kepler-1625b has radius consistent with that of Jupiter and an orbital period of 287 days.  The first evidence for the exomoon candidate, Kepler-1625b I, came from three transit observations from the \Kepler\ primary mission that showed FIXME \citep{teachey18a}...

@@

We fit the data with both the no-moon and models.  For the systematics, we tested the XY decorrelation model described above, but found that it did not perform as well as the systematics models presented in TK18 (10\% higher rms and time-correlated residuals).  We therefore opted to use a TK18 systematics model to enable a fair comparison between our results. We used a second-order polynomial trend in time, a constant offset after orbit 14 (where the guide stars are reacquired), and the non-parameteric orbit-long ramp model. This model has one more free parameter than the systematics model given in Equation~\ref{eq:sys}. Figure\,\ref{fig:bestfit} shows the best fit models.

Overall, we find that the TK18 fits have a larger rms than the fits to our new data reduction. The no-moon model has an rms of 381.5 ppm (compared to 362.2 for our data). As TK18 found, the moon model improves the rms to 363.4 ppm ($\Delta\chi^2 = 22.0$); however, even with the additional four free parameters, the moon model does not perform as well as the no-moon model fit to our data.  This difference in fit quality corresponds to $\Delta\mathrm{BIC} = 23.9$, which is strong evidence against the moon.  
%Even when a moon is included, the fit is still slightly worse (rms of 363.4 ppm) than our best no-moon model, in spite of four additional free parameters.

The moon model also yields qualitatively different posterior distributions for the two data sets.  For the TK18 data, the moon radius and transit time are peaked at $r_\mathrm{moon} = 4.0^{+0.8}_{-0.6}\,R_\oplus$ ($>2.1\,R_\oplus$ at $3\sigma$ confidence), and $t_\mathrm{moon} =  2458056.29^{+0.06}_{-0.04}\,\mathrm{BJD_{TDB}}$ (as shown in Figure\,\ref{fig:corner}). By contrast, the fit to the new data only yields an upper limit on the moon radius of ($4.0\,R_\oplus$ at $3\sigma$ confidence), and the transit time is unconstrained.

%Our results are consistent with those originally published in TK18, including the large improvement in $\chi^2$ when the moon is included ($\Delta\chi^2 = 22.0$). The posterior distribution for

%We obtain a better fit (a lower $\chi^2$) with the no-moon model fit to our data than we obtain with the moon model fit to the TK18 data, even though it has four additional free parameters.

\begin{figure}
\includegraphics[width = 0.5 \textwidth]{figures/fig5_pairs.pdf}
    \caption{Posterior distributions for the moon radius and time of transit based on an MCMC fit to data from this work (blue) and from TK18 (red). The shading corresponds to $1-$, $2-$, and $3\sigma$ contours (darkest to lightest). These values are marginalized over all other model parameters. The diagonal shows the normalized posterior probability density.}
\label{fig:corner}
\end{figure}

\section{Discussion}
We  do not recover the moon
differs both in the data reduction and the choice of systematics model
neither

many choices
rotate the image, aperture choice, measurement of the background, outlier masking,

\section{Conclusion}
In this work, we presented an independent analysis of HST observations of the Kepler-1625 system. In contrast to previous analysis by \citep{teachey18b}, we do not find evidence for the transit of a moon.

what is 
approach to data reduction was very similar, but of the data reduction, and

\acknowledgments
The HST data presented in this paper were obtained from the Mikulski Archive for Space Telescopes (MAST). STScI is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS5-26555. Support for MAST for non-HST data is provided by the NASA Office of Space Science via grant NNX13AC07G and by other grants and contracts.  We also use data from the European Space Agency (ESA) mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed by the {\it Gaia} Data Processing and Analysis Consortium (DPAC, \url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the DPAC has been provided by national institutions, in particular the institutions participating in the {\it Gaia} Multilateral Agreement.  We also use data products from the Two Micron All Sky Survey, which is a joint project of the University of Massachusetts and the Infrared Processing and Analysis Center/California Institute of Technology, funded by the National Aeronautics and Space Administration and the National Science Foundation.  This research has made use of the SIMBAD database, operated at CDS, Strasbourg, France; the REBOUND integrator package \citep{rein12}; the NumPy package \citep{van2011numpy}; and NASA's Astrophysics Data System.

@@

>>>>

\begin{abstract}
    Observations of the Kepler-1625 system with the Kepler and Hubble Space Telescopes have suggested the presence of a candidate exomoon, Kepler-1625b I, a Neptune-radius satellite orbiting a long-period Jovian planet. Here we present a new analysis of the Hubble observations, using an independent data reduction pipeline. We find that the transit light curve is well fit with a planet-only model, with a best-fit $\chi^2_\nu$ equal to $1.01$. The addition of a moon does not significantly improve the fit quality. We compare our results directly with \cite{teachey18b}, and find that we obtain a better fit to the light curve using a model with fewer free parameters (no moon). We discuss possible sources for the discrepancy in our results, and conclude that there is no single explanation for the difference but rather that it is the sum of many small choices. We conclude that future follow-up efforts for exomoons should focus on alternate targets.

\end{abstract}

\keywords{planets and satellites: individual (Kepler-1625b I)}

@@

Recently, a potential exomoon candidate was identified in the Kepler-1625 system \citep{teachey18a}. The host planet, Kepler-1625b has radius consistent with that of Jupiter and an orbital period of 287 days.  The first evidence for the exomoon candidate, Kepler-1625b I, was based on transit observations from \Kepler, which were discrepant with a planet-only model at $>4\sigma$ confidence \citep{teachey18a}. Follow-up observations with HST also suggested evidence for a moon, based on a small drop in the system flux after the planet's egress from transit \citep{teachey18b}. The best fit moon had a large radius (comparable to that of Neptune), and if real, would be unlike any moon in the Solar System.

Recently, \cite{rodenbeck18} performed an independent fit to the Kepler light curves and found that the evidence for the moon was strongly dependent on the detrending method. Motivated by this result, in this work we perform an independent fit to the HST light curve.

@@

We fit the data with both the no-moon and models.  For the systematics, we tested the XY decorrelation model described above, but found that it did not perform as well as the systematics models presented in TK18 (10\% higher rms and time-correlated residuals).  We therefore opted to use a TK18 systematics model to enable a fair comparison between our results. We obtained the best fit using a second-order polynomial trend in time, a constant offset after orbit 14 (where the guide stars are reacquired), and the non-parameteric orbit-long ramp model. This model has one more free parameter than the systematics model given in Equation~\ref{eq:sys}. Figure\,\ref{fig:bestfit} shows the best fit models.

Similar to the findings of TK18, the moon model improved the fit quality by a $\Delta\chi^2 = 22.0$. Notably, however, the moon model fit to the TK18 data does not perform better than the no-moon model fit to our new data (rms of 363 versus 356 ppm), even with the additional four free parameters.  This difference in fit quality corresponds to $\Delta\mathrm{BIC} = 31.2$, which is strong evidence against the moon.

The moon model also yields qualitatively different posterior distributions for the two data sets.  As shown in Figure\,\ref{fig:corner}, for the TK18 data the moon radius and transit time are peaked at $r_\mathrm{moon} = 4.0^{+0.8}_{-0.6}\,R_\oplus$  and $t_\mathrm{moon} =  2458056.29^{+0.06}_{-0.04}\,\mathrm{BJD_{TDB}}$. By contrast, the fit to the new data presented here yields an upper limit on the moon radius of ($4.0\,R_\oplus$ at $3\sigma$ confidence), and the transit time is unconstrained.

\begin{figure}
\includegraphics[width = 0.5 \textwidth]{figures/fig5_pairs.pdf}
    \caption{Posterior distributions for the moon radius and time of transit based on an MCMC fit to data from this work (blue) and from TK18 (red). The shading corresponds to $1-$, $2-$, and $3\,\sigma$ contours (from darkest to lightest). These values are marginalized over all other model parameters.} 
\label{fig:corner}
\end{figure}

\section{Discussion}
A natural question arising from our results is what the difference is between TK18 and the new fits presented here. One possibility is that the source of the discrepancy is the raw data itself. As shown in Figure\,\ref{fig:raw}, our measured count rate ranges from $2.46 -2.74\%$ lower than the TK18 measurement, and there is a small bump in the difference between the two data sets near the location of the moon transit identified in the TK18 data (see the bottom panel).

 We explored several modifications to our pipeline to attempt to reproduce the TK18 reduction. These included rotating the image by 0.5 degrees, using the same aperture as TK18 to extract the spectrum, and scaling the master sky flat for the background subtraction (rather than just subtracting the median). None of these modifications had a significant effect on our results.

There are a few other steps in the TK18 data reduction that would require substantial modification of our pipeline to recreate, but seem unlikely to be responsible for the difference. One of these is outlier masking. TK18 identify outliers with a Gaussian process fit to the pixel-level light curves, compared to our optimal extraction approach. Despite the difference, both methods flag $\sim$0.01\% of pixels as bad.  We also do not use the STScI software \texttt{axeprep} to embed the raw $256\times256$ image in a larger array; however, this process primarily affects the edge of the image, many pixels distant from the extraction box, so it is unclear how this step would bias the light curve.

 %The only other difference we identify in the data reduction is the outlier masking. In our analysis, we iteratively masked outliers with the optimal extraction routine, whereas TK18 identified outliers via a Gaussian process fit to the pixel-level light curves. We flagged 0.07\% of pixels as bad, whereas TK18 flag twice as many. It is possible that this discrepancy could play role in the difference between the raw data sets.

In addition to these differences in data reduction, we also used a new detrending model. We opted for a decorrelation against X and Y position, motivated by known variation in the sensitivity of individual pixels on the detector and the presence of small shifts in the position of the spectrum (see Figure\,\ref{fig:shifts}). We applied this detrending model to the TK18 data, and obtained a poor fit to the light curve compared to the polynomial detrending (for the moon model with X-Y decorrelation, the rms was 404 ppm). We did not recover a large moon in this fit (the best fit was $r_\mathrm{moon} = 1.2R_\oplus$), but there was correlated noise present in the data that precluded a robust measurement of the uncertainty on the moon radius for this model. The poor quality of the fit points toward the raw data as the culprit for the difference in our results, but as we discuss, we could not identify a specific choice in the data reduction that is responsible.

 We conclude that no single choice in the data reduction or the modeling provides an easy explanation for the difference in our results, but rather that the difference is in the sum of many subtle choices.

\section{Conclusion}
The hunt for exomoons remains exciting and volatile. Our analysis of the exomoon candidate Kepler-1625b I shows that the evidence in favor of the moon is highly sensitive to details of the data reduction and modeling. Future allocation of follow-up resources should prioritize alternative targets.

%\vspace{2cm}

\acknowledgments
The HST data presented in this paper were obtained from the Mikulski Archive for Space Telescopes (MAST). STScI is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS5-26555. Support for MAST for non-HST data is provided by the NASA Office of Space Science via grant NNX13AC07G and by other grants and contracts.  We also use data from the European Space Agency (ESA) mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed by the {\it Gaia} Data Processing and Analysis Consortium (DPAC, \url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the DPAC has been provided by national institutions, in particular the institutions participating in the {\it Gaia} Multilateral Agreement.  %We also use data products from the Two Micron All Sky Survey, which is a joint project of the University of Massachusetts and the Infrared Processing and Analysis Center/California Institute of Technology, funded by the National Aeronautics and Space Administration and the National Science Foundation.  This research has made use of the SIMBAD database, operated at CDS, Strasbourg, France; the REBOUND integrator package \citep{rein12}; the NumPy package \citep{van2011numpy}; and NASA's Astrophysics Data System.

@@

\bibitem[{{Rodenbeck} {et~al.}(2018){Rodenbeck}, {Heller}, {Hippke}, \&
  {Gizon}}]{rodenbeck18}
{Rodenbeck}, K., {Heller}, R., {Hippke}, M., \& {Gizon}, L. 2018, \aap, 617,
  A49, \dodoi{10.1051/0004-6361/201833085}

### 2019-01-23 ms.tex
v1

\begin{abstract}
    Observations of the Kepler-1625 system with the Kepler and Hubble Space Telescopes have suggested the presence of a candidate exomoon, Kepler-1625b-i, a Neptune-radius satellite orbiting a long-period Jovian planet. Here we present a new analysis of the Hubble observations from an independent data reduction pipeline. We find that the transit light curve is well fit with a planet-only model, with a best-fit $\chi^2_\nu$ equal to $1.01$. The addition of a moon does not significantly improve the fit quality. We compare our results directly with \cite{teachey18b}, and find that we obtain a better fit to the light curve using a model with fewer free parameters (no moon). We discuss possible sources for the discrepancy in our results, and conclude that there is no single explanation for the difference but rather that it is the sum of many small choices. We conclude that future follow-up efforts for exomoons should focus on alternate targets.

@@

\keywords{planets and satellites: individual (Kepler-1625b)}

@@

\section{Conclusion}
The hunt for exomoons remains exciting and volatile. Our analysis of the exomoon candidate Kepler-1625b-i shows that the evidence in favor of the moon is highly sensitive to details of the data reduction and modeling. Future allocation of follow-up resources should prioritize alternative targets.

@@

\acknowledgments
The HST data presented in this paper were obtained from the Mikulski Archive for Space Telescopes (MAST). STScI is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS5-26555. Support for MAST for non-HST data is provided by the NASA Office of Space Science via grant NNX13AC07G and by other grants and contracts.  We also use data from the European Space Agency (ESA) mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed by the {\it Gaia} Data Processing and Analysis Consortium (DPAC, \url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the DPAC has been provided by national institutions, in particular the institutions participating in the {\it Gaia} Multilateral Agreement.  We also use data products from the Two Micron All Sky Survey, which is a joint project of the University of Massachusetts and the Infrared Processing and Analysis Center/California Institute of Technology, funded by the National Aeronautics and Space Administration and the National Science Foundation.  This research has made use of the SIMBAD database, operated at CDS, Strasbourg, France; the REBOUND integrator package \citep{rein12}; the NumPy package \citep{van2011numpy}; and NASA's Astrophysics Data System.

>>>>

\begin{abstract}
    Observations of the Kepler-1625 system with the Kepler and Hubble Space Telescopes have suggested the presence of a candidate exomoon, Kepler-1625b I, a Neptune-radius satellite orbiting a long-period Jovian planet. Here we present a new analysis of the Hubble observations, using an independent data reduction pipeline. We find that the transit light curve is well fit with a planet-only model, with a best-fit $\chi^2_\nu$ equal to $1.01$. The addition of a moon does not significantly improve the fit quality. We compare our results directly with \cite{teachey18b}, and find that we obtain a better fit to the light curve using a model with fewer free parameters (no moon). We discuss possible sources for the discrepancy in our results, and conclude that there is no single explanation for the difference but rather that it is the sum of many small choices. We conclude that future follow-up efforts for exomoons should focus on alternate targets.

@@

\keywords{planets and satellites: individual (Kepler-1625b I)}

@@

\section{Conclusion}
The hunt for exomoons remains exciting and volatile. Our analysis of the exomoon candidate Kepler-1625b I shows that the evidence in favor of the moon is highly sensitive to details of the data reduction and modeling. Given that we achieve an excellent fit to the light curve with a no-moon model, and that the addition of a moon does not significantly improve the fit quality, we conclude that future allocation of follow-up resources for exomoons should prioritize alternate targets.

@@

\acknowledgments
The HST data presented in this paper were obtained from the Mikulski Archive for Space Telescopes (MAST). STScI is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS5-26555. Support for MAST for non-HST data is provided by the NASA Office of Space Science via grant NNX13AC07G and by other grants and contracts.  We also use data from the European Space Agency (ESA) mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed by the {\it Gaia} Data Processing and Analysis Consortium (DPAC, \url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the DPAC has been provided by national institutions, in particular the institutions participating in the {\it Gaia} Multilateral Agreement.  
%We also use data products from the Two Micron All Sky Survey, which is a joint project of the University of Massachusetts and the Infrared Processing and Analysis Center/California Institute of Technology, funded by the National Aeronautics and Space Administration and the National Science Foundation.  This research has made use of the SIMBAD database, operated at CDS, Strasbourg, France; the REBOUND integrator package \citep{rein12}; the NumPy package \citep{van2011numpy}; and NASA's Astrophysics Data System.
